---
title: "CRARS and RAD Lab Soil Intake Progress Report"
format: 
  html:
    theme: pulse
    toc: true
    toc-location: right
editor: visual
execute: 
  warning: false
  message: false
  echo: false
---
```{r, echo = FALSE}
# Load necessary packages
library(tidyverse)
library(knitr)
library(lubridate)
library(googlesheets4)
library(googledrive)
library(ggpubr)

# Load example Barcode Sheet
sample_data <- read_sheet('https://docs.google.com/spreadsheets/d/1PCCSZJhs9f4raQyxGGcWhFUCayHHUjMhjVCcoVDrWaI/edit#gid=718808986')

#sample_duration <- sample_data %>% 
  #group_by(Barcode) %>% summarize(duration = difftime(max(Timestamp) - min(Timestamp)))

sample_data$Timestamp <- lubridate::ymd_hms(sample_data$Timestamp, tz = "UTC")

sample_data$`Sample Status` <- fct_relevel(sample_data$`Sample Status`, c("Recieved", "Sieved & Grinded", "Vialed", "Pre- transport Check"))


sample_wide <- sample_data %>% pivot_wider(names_from = In_out, values_from = Timestamp)

grouped_data1 <- sample_wide %>%
  mutate(Time = as.numeric(difftime(Out, In, units = "hours")))

# Group Samples by most recent entry 
grouped_data <- sample_data %>%
  group_by(Barcode) %>%
  slice_tail(n = 1) %>%
  ungroup()

# Group data into the 4 categories 
recieved <- grouped_data %>%
  filter(`Sample Status`  == "Recieved") %>%
  select(Barcode, Employee, Timestamp)

SandG <- grouped_data %>%
  filter(`Sample Status`  == "Sieved & Grinded") %>%
  select(Barcode, Employee, Timestamp)

vialed <- grouped_data %>%
  filter(`Sample Status`  == "Vialed") %>%
  select(Barcode, Employee, Timestamp)

preT <- grouped_data %>%
  filter(`Sample Status`  == "Pre- transport Check") %>%
  select(Barcode, Employee, Timestamp)
```

# Purpose of this Report

The purpose of this report is to provide the `Center of Regenaterive Agriculture and Resiliant Systems` ( CRARS ) and the `Regenerative Agriculture Demonstration Lab` ( RAD Lab ) with a comprehensive report of the status of newly received soil samples and where they are in the process of intake processing before being sent for analysis. 


# Workflow of Tracker

```{mermaid}
flowchart LR
  A[Google Form] --> B[Google Sheet]
  B --> C{Quarto Document}
  C --> D[HTML Report]
```

::: {.border}

# Current Progress  

## Samples Processed to date

* This section of the report intends to display tables of where each sample is in the "Intake Process" ( i.e. `Received`, `Sieved & Grinded`, `Vialed`, `Pre-transport check`).

```{r, echo = FALSE}
kable(recieved, caption = "Recieved", align = "c", booktabs = TRUE)

```

```{r, echo = FALSE}
kable(SandG, caption = "Sieved & Grinded", align = "c", booktabs = TRUE)

```

```{r, echo = FALSE}
kable(vialed, caption = "Vialed", align = "c", booktabs = TRUE)

```

```{r}
kable(preT, caption = "Pre-Transport Check", align = "c", booktabs = TRUE)
```

## Distribution of Samples Across Stages

* This section will show the distribution of samples in each of the intake processes. 

```{r}
status_table <- grouped_data %>%
  group_by(`Sample Status`) %>%
  summarize(count = n())

# factor(status_table$`Sample Status`, levels = c("Received", "Sieved & Grinded", "Vialed", "Pre-transport check"), ordered = TRUE)

ggplot(status_table, aes(x = `Sample Status`, y = count, fill = `Sample Status`)) +
  geom_bar(stat = "identity") +
  xlab("Sample status") +
  ylab("Number of samples") +
  ggtitle("Sample status distribution") +
  theme_classic() +
  scale_fill_brewer(palette = "YlOrRd")
```

## Location of Active Samples

* This scatter plot shows the active samples in the intake process, where they are in the process, and also provides a date that they were entered.

```{r}
# Scatterplot of Active Samples
grouped_data$Timestamp <- as.Date(grouped_data$Timestamp)

ggplot(data = grouped_data, aes(x = Timestamp, y = Barcode, color = `Sample Status`)) +
  geom_point() +
  scale_color_discrete(name = "Sample Status") +
  labs(x = "Time", y = "Sample", title = "Samples In Progress") +
  theme_classic() +
  scale_x_date(date_labels="%b %d", breaks = unique(grouped_data$Timestamp)) +
  theme(axis.text.x = element_text(angle=90, hjust=1)) 
  

```

## Progress of Samples

* This section simply shows the reader a progress linebar where as a sample goes through the intake the line will progress from left to right. 

```{r}

grouped_data1$`Sample Status` <- fct_relevel(grouped_data1$`Sample Status`, c("Recieved", "Sieved & Grinded", "Vialed", "Pre- transport Check"))

ggplot(data = grouped_data1, aes(x = `Sample Status`, y = Barcode, group = Barcode, color = `Sample Status`)) +
  geom_point() + 
  geom_line()+
  theme(legend.position = "none")

```
:::

# Time Between Intake Processes

## Progress bar with time intervals

* This graph shows the progress of the samples through the intake system as well as the time each sample took in each process.
```{r}
grouped_data1$`Sample Status` <- fct_relevel(grouped_data1$`Sample Status`, c("Pre- transport Check", "Vialed", "Sieved & Grinded", "Recieved"))
# Create the progress plot
ggplot(data = grouped_data1, aes(x = Time, y = Barcode, fill = `Sample Status`)) +
  geom_col()+
  scale_fill_brewer(palette = "YlOrRd")
```


## Box plot of time between sample input

In this visual we show a box plot of the time distribution between process for everysample. Although we cannot see specific samples we can see where they lie within the distribution. 

```{r}
grouped_data1$`Sample Status` <- fct_relevel(grouped_data1$`Sample Status`, c("Recieved", "Sieved & Grinded", "Vialed", "Pre- transport Check"))


ggboxplot(grouped_data1, "Sample Status", "Time",
    color = "Sample Status", palette = get_palette("YlOrRd",4),
    add = "jitter", shape = "Sample Status")
```






